Probabilistic Forecast Reconciliation

### 2018-08-08 Presentation/ProbForeRec.tex
updated presentation up to probabilistic

\date{June 20, 2018}

@@

@@

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear map.  Then 

>>>>

\date{August 15, 2018}

@@

  \begin{frame}{Coherent Point Forecast}
  	A {\bf coherent point forecast} is any forecast lying in the linear subspace $\mathfrak{s}$
  \begin{frame}{Reconciled Point Forecast}
  Let $\hat{\bm y}\in\mathbb{R}^n$ be an incoherent forecast and $g(.)$ be a function $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$.
	A {\bf point forecast} $\tilde{\bm y}$ is reconciled with respect to $g(.)$ iff 
    \tilde{\bm y}={\bm S}g(\hat{\bm y})
  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}{\bm y}$
  \begin{frame}{Special Case: Projection}
   \item An important special case is where ${\bm S}{\bm G}$ is a projection.
  	\item ${\bm S}{\bm G}$ is symmetric
  	\item ${\bm S}{\bm G}$ is idempotent
  \item Let ${\bm v}\in\mathfrak{s}$ 
    	\item ${\bm S}{\bm G}{\bm v}$ will also lie in $\mathfrak{s}$.
    	\item ${\bm S}{\bm G}{\bm v}={\bm v}$ only when ${\bm S}{\bm G}$ is a projection.

@@

  \begin{frame}{Projections preserve unbiasedness}
	Let $\hat{\bm y}_{t+h|t}$ be an unbiased forecast that is $E_{1:t}(\hat{\bm y}_{t+h|t})={\bm \mu_{t+h|t}}$ where ${\bm \mu_{t+h|t}}=E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$
	  The reconciled forecast $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ will also be unbiased iff ${\bm S}{\bm G}$ is a projection.
    Previously, this was often stated as an assumption that ${\bm S}{\bm G}{\bm S}={\bm S}$.    
  \begin{frame}{Proof}
  Very easy proof
  E_{1:t}(\tilde{\bm{y}}_{t+h|t})
  &= E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})\\
  &= \bm{S}\bm{G}E_{1:t}(\hat{\bm{y}}_{t+h|t})\\
  &= \bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
  &= \bm{\mu}_{t+h|t}
  The last equality does not hold for ${\bm G}$ in general.
  \begin{frame}{Why reconciliation works}
  	\item The realised observation always lies on $\mathfrak{s}$.
  	\item Orthogonal projections always get us `closer' to all points in $\mathfrak{s}$ including the actual realisation.
  	\item Ergo reconciliation reduces the error, not only in expectation, but always. 
  	\item Oblique projections have the same property for non-Euclidean distance. 

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear function.  Then 
